---
title: "Simple Regression Analysis on Fuel Economy dataset"
author: "Ashish S Shanbhag"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
The datasets contain different estimates of fuel economy for passenger cars and trucks. For each vehicle, various
characteristics are recorded such as the engine displacement or number of cylinders. Along with these values,
laboratory measurements are made for the city and highway fuel economy (FE) of the car.

This project explains as to how Fuel Efficiency is dependent on Engine Displacement.

Step 1 : Load the given dataset.

```{r}
library(readr)
FE2010 <- read_csv("FE2010.csv")
```

Step 2 : Perform linear regression.

```{r}
library(knitr)
model<-lm(FE2010$`Fuel efficiency(Y)` ~ FE2010$`EngDisplacement(X)`)
model
```

here are two co-efficients one is intercept and one more is regression co-efficient named engine displacement(x).

Let us name intercept as b0 and regresion co-efficient as b1.

The calculations are explained below

![](D:/Acadgild study materials/ACADGILD_Projects/1.1 simple regression analysis on fuel economy/fuel/Screenshot (79).png)

the above values are computed in the file FE2010.xlsx can be found in my GitHub.

![](D:/Acadgild study materials/ACADGILD_Projects/1.1 simple regression analysis on fuel economy/fuel/Screenshot (80).png)

![](D:/Acadgild study materials/ACADGILD_Projects/1.1 simple regression analysis on fuel economy/fuel/Screenshot (81).png)

The detailed calculations are found in FE2010.xlsx in my GitHub


Step 3 : Plot the linear model.

```{r}
library("ggplot2")
ggplot() +
  geom_point(aes(x=FE2010$`EngDisplacement(X)`,y=FE2010$`Fuel efficiency(Y)`),colour='red')+
  geom_line(aes(x=FE2010$`EngDisplacement(X)`,y=predict(model,newdata = FE2010)),colour='blue')+
  ggtitle('FUEL ECONOMY VS ENGINE DISPLACEMENT')+
  xlab('Engine Displacement')+ylab('Fuel Economy')

```

Now we have to substitute b0 and b1 in regression equation

y=a+bX

y=b0+b1X

Fuel Efficiency = 50.563 - 4.5209 * EngineDisplacement

The above statement states that inorder to increase Fuel Efficiency by 1 unit,then Engine Displacement has to be decreased by 4.5 units.

Step 4 : Now plot the summary of the model

```{r}
summary(model)
```
![](D:/Acadgild study materials/ACADGILD_Projects/1.1 simple regression analysis on fuel economy/fuel/Screenshot
(84).png)

SST stands for Sum Squared Total.
SSR stands for Sum Squared Regressor.
SSE stands for Sum Squared Error.

![](D:/Acadgild study materials/ACADGILD_Projects/1.1 simple regression analysis on fuel economy/fuel/Screenshot (82).png)

![](D:/Acadgild study materials/ACADGILD_Projects/1.1 simple regression analysis on fuel economy/fuel/Screenshot (85).png)

